---
title: "What do students think about a campus-wide ban on signle-use cups at cafeterias and kiosks?"
subtitle: "Analysis of a non-representative survey of students in Zurich"
date: 2024-06-06
author:
  - name: Till Häussner
    orcid: 0009-0005-7617-9312
    email: thaeussner@student.ethz.ch
    affiliation: 
      - name: ETH Zürich
        url: www.ethz.ch
abstract: > 

number-sections: true
  
keywords:
  - Waste Reduction
  - Single-Use Cups
  - Students
  - University Campus
  
format:
  html:
    code-fold: true
    toc: true
    html-math-method: katex
    css: styles.css
    
    

license: "CC BY"
funding: "The author received no specific funding for this work."
---

```{r}
#| warning: false

library(tidyverse)
library(knitr)
library(kableExtra)
library(scales)
library(ggthemes)
library(ggExtra)

df <- read_rds(here::here("data/processed/processed_data.rds"))

df_summary <- df |> 
  summarize(answers = n(),
            avg_age = mean(age, na.rm = TRUE),
            std_age = sd(age, na.rm = TRUE),
            avg_importance_recycling = mean(importance_recycling, na.rm = TRUE),
            std_importance_recycling = sd(importance_recycling, na.rm = TRUE),
            avg_importance_waste_reduction = mean(importance_waste_reduction, na.rm = TRUE),
            std_importance_waste_reduction = sd(importance_waste_reduction, na.rm = TRUE),
            avg_ban_support = mean(singleusecup_ban_support, na.rm = TRUE),
            std_ban_support = sd(singleusecup_ban_support, na.rm = TRUE),
            avg_ban_impact = mean(singleusecup_ban_impact, na.rm = TRUE),
            std_ban_impact = sd(singleusecup_ban_impact, na.rm = TRUE),
            avg_multiusecup_deposit = mean(multiusecup_deposit, na.rm = TRUE),
            std_multiusecup_deposit = sd(multiusecup_deposit, na.rm = TRUE))

df_summary_long <- df_summary |> 
  pivot_longer(cols = answers:std_multiusecup_deposit,
               names_to = "variable",
               values_to = "value")

```

# Introduction {#sec-introduction}

Introduction section with 3 to 5 sentences introduces the context within which the data was created.

# Methods {#sec-methods}

The data was obtained using a Google Forms survey. Questions were split into three sections, about 1) general info, 2) their habits with single-use cups and 3) their opinions and further thoughts on a campus-wide ban on single-use cups, the results of which can be found in @sec-respondents, @sec-habits, and @sec-opinions. Over the span of nine days from 2024-05-21 to 2024-05-29, students were asked on campus or online to fill out the questionnaire. The answers were automatically gathered in Google Sheets and from there converted to csv and rds using /R/01-data_download.R.

It is important to note that this survey can not be considered representative, as I mainly prompted friends and colleagues to complete the survey and did not distribute this survey widely across campus or further, and thus **this is just a quick, non-representative collection of opinions.**

# Results {#sec-results}

Figures and tables in Results section are interpreted with 2 to 3 sentences each.

Let's look at the results. The anonymized raw data (@tbl-rawdata) can be found in @sec-data in the appendix, where we can see that we received 40 answers to 16 relevant questions. Important, numeric variables are summarized in @tbl-summary below and will be used throughout this chapter.

```{r}
#| label: tbl-summary
#| tbl-cap: "Summarizing stats for the survey"

df_summary_long |> 
  kable() |> 
  kable_styling()
```

## Respondents {#sec-respondents}

In the first section, respondents were asked to state their age, study field and level, and their institution. In @fig-respondents-institution-1, we can see that most answers came from people within Engineering at ETH, and that all respondents were in their 20s as seen in @fig-respondents-institution-2, with an average age of `{r} df_summary_long[2, 2] ` and a standard deviation of `{r} df_summary_long[3, 2] ` years.

```{r}
#| layout-ncol: 2
#| label: fig-respondents-institution
#| fig-cap: "Distribution of responses"
#| fig-subcap: 
#|   - "Institutions of respondents"
#|   - "Age distribution of respondents"
#| warning: false

ggplot(data = df, 
       mapping = aes(x = reorder(institution, institution, length),
                     fill = field)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Institution",
       y = "Number of responses (total: 40)",
       fill = "Study field") +
  theme_minimal() +
  scale_fill_colorblind()

# using this answer from Stackoverflow for the labeled average: https://stackoverflow.com/questions/61701985/how-to-add-text-to-geom-vline-in-ggplot
ggplot(data = df) +
  geom_bar(mapping = aes(x = age,
                     fill = field)) +
  geom_vline(xintercept=23.425, color="black",  linetype = "dashed", size=0.5) +
  geom_label(x=23.425, y=0, label="Average: 23.425", vjust=-0.25) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  labs(x = "Age (average: 23.4)",
       y = "Number of responses (total: 40)",
       fill = "Study field") +
  theme_minimal() +
  scale_fill_colorblind() +
  geom_boxplot(mapping = aes(x = age), alpha = 0.2, position = position_nudge(y=2.5), width = 2)

```

In @fig-respondents-detail, the study level is added as well, showing us that most respondents are indeed studying engineering at Bachelor's or Master's level at ETH Zürich, with very few outliers.

```{r}
#| label: fig-respondents-detail
#| fig-cap: "Position, Institution, Age and Field of Respondents"
#| warning: false

df <- df |> 
  mutate(position = factor(position, levels = c("Bachelor (BSc/BA)", "Master (MSc/MA)", "PhD / Doctorate", "Employee")))

ggplot(data = df, 
       mapping = aes(x = position,
                     y = age,
                     color = field)) +
  geom_jitter(size = 3, alpha = 0.6, width = 0.3, height = 0.2) +
  coord_flip() +
  labs(x = "Study level",
       y = "Age (average: 23.4)",
       color = "Study field") +
  facet_wrap(~institution) +
  theme_minimal() +
  scale_color_colorblind()

```

In the next questions, the respondents were asked to rank 1) the general importance of waste reduction and 2) the general importance of recycling on a scale of 1 (not important at all) to 5 (very important). The answers are summarized in @fig-respondents-opinions, where it can be seen that both are perceived as important by most, with waste reduction having a higher mean importance than recycling.

```{r}
#| label: fig-respondents-opinions
#| fig-cap: "Opinions on waste reduction and recycling in general"
#| fig-subcap: "Rated on a scale from 1 (I don't care) to 5 (I think it's very important)"
#| warning: false


ggplot(data = df) +
  geom_jitter(mapping = aes(x = importance_waste_reduction,
                     y = importance_recycling,
                     color = field),
              size = 3, alpha = 0.6, width = 0.25, height = 0.25) +
  geom_boxplot(mapping = aes(x = importance_waste_reduction),
               alpha = 0.2, position = position_nudge(y=1.75), width = 0.75) +
  geom_boxplot(mapping = aes(y = importance_recycling),
               alpha = 0.2, position = position_nudge(x=1.75), width = 0.75) +
  labs(x = "General importance of waste reduction (average: 4.48)",
       y = "General importance of recycling (average: 4.33)",
       color = "Study field") +
  theme_minimal() +
  scale_color_colorblind()

```

## Single-use cup habits {#sec-habits}

When asked about their habits with buying drinks single-use cups on campus, most respondents answered that they never or occasionally bought single-use cups, and if they did, the overwhelming majority choose "convenience" as their main reason as seen in @fig-habits.

```{r}
#| label: fig-habits
#| layout-ncol: 2
#| fig-cap: "Single-use cup usage frequency and main reason"
#| fig-subcap: 
#|   - "Frequency and main reason"
#|   - "Frequency and study program"
#| warning: false


df <- df |> 
  mutate(singleusecup_frequency = factor(singleusecup_frequency, levels = c("I don't know", "Multiple times per day", "Every day", "About once a week", "Occasionally", "Never"))) |> 
  mutate(singleusecup_reason = factor(singleusecup_reason, levels = c("Convenience", "Hygiene", "Aesthetics", "Price (single-use cups are free as opposed to multi-use cups)", "I don't think about it", "I never use single-use cups")))

ggplot(data = df,
       mapping = aes(x = singleusecup_frequency,
                     fill = singleusecup_reason)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_fill_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "How often do you buy single-use cups on campus?",
       y = "Number of responses (total: 40)",
       fill = "Main reason") +
  theme_minimal()

ggplot(data = df,
       mapping = aes(x = singleusecup_frequency,
                     fill = position)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_brewer() +
  labs(x = "How often do you buy single-use cups on campus?",
       y = "Number of responses (total: 40)",
       fill = "Study program") +
  theme_minimal()


```

Depending on personal preferences or other factors, a ban on single-use cups can have an impact on daily life. When asked to rank this impact on a scale of 1 ("I wouldn't notice") to 5 ("It would have a negative impact on my daily life"), most respondents answered 1 ("I wouldn't notice") as seen in @fig-impact (a). In @fig-impact (b) these results are complemented with the previous answer about the usage frequency, revealing that generally - the more respondets bought drinks in single-use cups, the higher they would consider the negative impact on their daily life.

```{r}
#| label: fig-impact
#| fig-cap: "The impact of a ban on daily life, rated from 1 (I wouldn't notice) to 5 (It would have a negative impact on my daily life)"
#| layout-ncol: 2
#| fig-subcap: 
#|   - "Ban impact on daily life"
#|   - "Ban impact on daily life, with single-use cup usage frequency"
#| warning: false

ggplot(data = df) +
  geom_bar(mapping = aes(x = singleusecup_ban_impact,
                     fill = singleusecup_reason)) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_impact), color = "red",
               alpha = 0.2, position = position_nudge(y=2.75), width = 3) +
  geom_vline(xintercept=2.025, color="darkgrey",  linetype = "dashed", size=0.5) +
  geom_label(x=2.025, y=0, label="Average: 2.025", vjust=-0.25) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "How would a ban impact your daily life? (average: 2.03)",
       y = "Number of responses (total: 40)",
       fill = "Main reason") +
  theme_minimal() +
  scale_fill_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups"))



ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_impact,
                            y = singleusecup_frequency,
                            color = singleusecup_reason),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_impact),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  geom_vline(xintercept=2.025, color="darkgrey",  linetype = "dashed", size=0.5) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "How would a ban impact your daily life? (average: 2.03)",
       y = "How often do you buy single-use cups on campus?",
       color = "Main reason") +
  theme_minimal()


```

## Opinions on a ban on single-use cups {#sec-opinions}

Lastly, what do respondents think about a ban on single-use cups? The question here was "Would you support a campus-wide ban on single-use cups at cafes, kiosks, cafeterias etc?", and the answer could be given on a scale from 1 ("No, absolutely not") to 5 ("Yes, absolutely"). @fig-support shows that there is no clear answer, but a slight trend towards yes with an average of 3.35 and a big standard deviation of 1.27.

```{r}
#| label: fig-support
#| fig-cap: "Support for a ban on single-use cups"
#| fig-subcap: "Rated on a scale from 1 (No, absolutely not) to 5 (Yes, absolutely)"
#| warning: false

ggplot(data = df) +
  geom_bar(mapping = aes(x = singleusecup_ban_support,
                     fill = singleusecup_reason)) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support), color = "red",
               alpha = 0.2, position = position_nudge(y=2.75), width = 3) +
  geom_vline(xintercept=3.35, color="darkgrey",  linetype = "dashed", size=0.5) +
  geom_label(x=3.35, y=0, label="Average: 3.35", vjust=-0.25) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Support for a ban on single-use cups from 1 to 5 (average: 3.35)",
       y = "Number of responses (total: 40)",
       fill = "Main reason") +
  theme_minimal() +
  scale_fill_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups"))

```
How do the habits with single-use cups influence the support for a ban? This is explored here, where @fig-support-detail-1 shows that the less single-use cups are used, the stronger the support for a ban is, but only slightly with a wide range. In @fig-support-detail-2, the trend between the perceived impact on daily life and support for a ban is shown. Unsurprisingly, the smaller the impact on daily life is perceived, the stronger a ban is supported in general.
```{r}
#| label: fig-support-detail
#| fig-cap: "Support for a ban on single-use cups, compared with habits"
#| layout-ncol: 2
#| fig-subcap: 
#|   - "Ban impact on daily life with usage frequency"
#|   - "Ban impact on daily life with impact on daily life"
#| warning: false



ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_support,
                            y = singleusecup_frequency,
                            color = singleusecup_reason),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  geom_smooth(mapping = aes(x = singleusecup_ban_support,
                            y = singleusecup_frequency), alpha = 0.2) +
  geom_vline(xintercept=3.35, color="darkgrey",  linetype = "dashed", size=0.5) +
  geom_label(x=3.35, y=1.5, label="Average: 3.35", vjust=0) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "Support for a ban on single-use cups from 1 to 5 (average: 3.35)",
       y = "How often do you buy single-use cups on campus?",
       color = "Main reason") +
  theme_minimal()

ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_support,
                            y = singleusecup_ban_impact,
                            color = singleusecup_reason),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  geom_boxplot(mapping = aes(y = singleusecup_ban_impact),
               alpha = 0.2, position = position_nudge(x=0.75), width = 0.5) +
  geom_smooth(mapping = aes(x = singleusecup_ban_support,
                            y = singleusecup_ban_impact), alpha = 0.2) +
  geom_vline(xintercept=3.35, color="darkgrey",  linetype = "dashed", size=0.5) +
  geom_label(x=3.35, y=4.5, label="Average: 3.35", vjust=0) +
  geom_hline(yintercept=2.025, color="darkgrey",  linetype = "dashed", size=0.5) +
  geom_label(x=1, y=2.025, label="Average: 2.025", hjust=0) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "Support for a ban on single-use cups from 1 to 5 (average: 3.35)",
       y = "Negative impact on daily life (average: 2.03)",
       color = "Main reason") +
  theme_minimal()


```

Now, if we look at support in terms of study field (@fig-support-study-1) and program (@fig-support-study-2), we can see no direct trend or tendency, but a wide range of opinions. This is probably also due to insufficient and non-respresentative data, but also reflects the fact that this topic is quite probably quite separate from personal work and study proferences.

```{r}
#| label: fig-support-study
#| fig-cap: "Support for a ban on single-use cups based on study program and field"
#| layout-ncol: 2
#| warning: false
#| fig-subcap: 
#|   - "Support for a ban based on study field"
#|   - "Support for a ban based on study field and program"

ggplot(data = df) +
  geom_bar(mapping = aes(x = singleusecup_ban_support,
                     fill = field)) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(y=2.75), width = 3) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Support for a ban on single-use cups from 1 to 5 (average: 3.35)",
       y = "Number of responses (total: 40)",
       fill = "Study field") +
  theme_minimal() +
  scale_fill_colorblind()



ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_support,
                            y = position,
                            color = field),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind() +
  labs(x = "Support for a ban on single-use cups from 1 to 5 (average: 3.35)",
       y = "Study program",
       color = "Study field") +
  theme_minimal()


```

We've seen that there is a slight support for a ban, but how should it be implemented? For this, participants were asked to state what options they needed to be available in case of a ban on single-use cups. @fig-options explores those results and shows that the option fo bring your own cups is strongly demanded by the large majority of respondents, with the option to sit down with proper ceramic cups and the option to get multi-use cups with a small deposit below 5 Fr. also being seen as important. More expensive options were not too popular, and also the idea of no available options - where a personal cup would need to be brought - was dismissed by most. 

```{r}
#| label: fig-options
#| fig-cap: "Without single-use cups, what alternatives or options need to be available?"
#| warning: false


df <- df |> 
  mutate(options_bring_own_cup = factor(options_bring_own_cup, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_sit_down = factor(options_sit_down, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_none = factor(options_none, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_multiusecup_small_deposit = factor(options_multiusecup_small_deposit, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_multiusecup_large_deposit = factor(options_multiusecup_large_deposit, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_multiusecup_to_buy = factor(options_multiusecup_to_buy, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know")))

df_options <- df |> 
  select(id, singleusecup_ban_support, singleusecup_ban_impact, options_bring_own_cup:options_none) |> 
  pivot_longer(cols = options_bring_own_cup:options_none,
               names_to = "option",
               values_to = "opinion") |> 
  mutate(option = factor(option, levels = c("options_none", "options_multiusecup_large_deposit", "options_multiusecup_to_buy", "options_multiusecup_small_deposit", "options_sit_down", "options_bring_own_cup")))

color_values <- scales::seq_gradient_pal("blue", "orange", "Lab")(seq(0,1,length.out=5))

ggplot(data = df_options,
       mapping = aes(x = option,
                     fill = opinion)) +
  geom_bar() +
  coord_flip() +
  scale_x_discrete(labels = c("No option; you have to bring your own cup", "Multi-use cups with a large deposit (> 5 Fr.)", "Multi-use cups that you have to buy (> 10 Fr.)", "Multi-use cups with a small deposit (< 5 Fr.)", "Sit down with ceramic cups at no extra costs", "You can bring your own cup")) +
  labs(x = "Option",
       y = "Number of answers (total: 40)",
       fill = "Opinion") +
  theme_minimal() +
  scale_fill_manual(values = color_values)


```
Lastly, does a small deposit on a multi-use cup have any effect, or will it just be thrown away and thus treated as a more expensive single-use cup? What deposit is large enough for multi-use cups? This was the last question, where  respondents were asked: "How high do you think a deposit on multi-use cups would need to be in order for them not to be thrown away?" and had to choose a value on a scale from 0 ("No deposit; nobody would throw away a free multi-use cup") to 10 ("10 Fr. or higher"). @fig-deposit shows that responses here were quite varied, with peaks at 2 and 5 Fr., which do not seem to depend too much on the main reason for using single-use cups, unlike initially assumed. @fig-deposit-support shows the same data but split up to show the dependency on the support for a single-use cup ban. There is no real trend to be seen and answers vary widely.

```{r}
#| label: fig-deposit
#| fig-cap: "How high would a deposit on multi-use cups need to be in order for them not to be thrown away?"
#| fig-subcap: "Rated on a scale from 0 (No deposit; nobody would throw away a free multi-use cup) to 10 (10 Fr. or higher)"
#| warning: false

ggplot(data = df) +
  geom_bar(mapping = aes(x = multiusecup_deposit,
                     fill = singleusecup_reason)) +
  geom_boxplot(mapping = aes(x = multiusecup_deposit), color = "red",
               alpha = 0.2, position = position_nudge(y=2.75), width = 3) +
  geom_vline(xintercept=4, color="darkgrey",  linetype = "dashed", size=0.5) +
  geom_label(x=4, y=0, label="Average: 4", vjust=-0.25) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  scale_x_continuous(breaks = seq(from = 0, to = 10, by = 1)) +
  labs(x = "Minimum deposit for a multi-use cup [Fr.]",
       y = "Number of responses (total: 40)",
       fill = "Main reason for using single-use cups") +
  theme_minimal() +
  scale_fill_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups"))

```

```{r}
#| label: fig-deposit-support
#| fig-cap: "How high would a deposit on multi-use cups need to be in order for them not to be thrown away?"
#| fig-subcap: "Rated on a scale from 0 (No deposit; nobody would throw away a free multi-use cup) to 10 (10 Fr. or higher)"
#| warning: false

ggplot(data = df) +
  geom_jitter(mapping = aes(x = multiusecup_deposit ,
                            y = singleusecup_ban_support,
                            color = singleusecup_reason),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = multiusecup_deposit),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  geom_boxplot(mapping = aes(y = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(x=0.75), width = 1) +
  geom_vline(xintercept=4, color="darkgrey",  linetype = "dashed", size=0.5) +
  geom_label(x=4, y=4.4, label="Average: 4", vjust=0) +
  geom_hline(yintercept=3.35, color="darkgrey",  linetype = "dashed", size=0.5) +
  geom_label(x=6, y=3.35, label="Average: 3.35", hjust=0) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "Minimum deposit for a multi-use cup [Fr.]",
       y = "Support for a ban on single-use cups from 1 to 5 (average: 3.35)",
       color = "Main reason for using single-use cups") +
  theme_minimal()

```


# Conclusions {#sec-conclusions}

Conclusions concisely summarize findings in a bullet point format.

-   aosbasda

-   asdasda

-   sdasdas

-   daasd

# Raw Data {.appendix} {#sec-data}

```{r}
#| label: tbl-rawdata
#| tbl-cap: "The full, anonymized raw data used for the visualizations."
df |> 
  select(!further_thoughts) |> 
  kable() |> 
  kable_styling()
```
