---
title: "What do students think about a campus-wide ban on signle-use cups at cafeterias and kiosks?"
subtitle: "Analysis of a non-representative survey of students in Zurich"
date: 2024-06-06
author:
  - name: Till Häussner
    orcid: 0009-0005-7617-9312
    email: thaeussner@student.ethz.ch
    affiliation: 
      - name: ETH Zürich
        url: www.ethz.ch
abstract: > 
  
keywords:
  - Waste Reduction
  - Single-Use Cups
  - Students
  - University Campus
  
format:
  html:
    code-fold: true
    toc: true
    html-math-method: katex
    css: styles.css
    
    

license: "CC BY"
funding: "The author received no specific funding for this work."
---

```{r}
#| warning: false

library(tidyverse)
library(scales)
library(ggthemes)
library(ggExtra)

df <- read_rds(here::here("data/processed/processed_data.rds"))



```

# Introduction

Introduction section with 3 to 5 sentences introduces the context within which the data was created.

# Methods

The data was obtained using a Google Forms survey. Over the span of nine days from 2024-05-21 to 2024-05-29, students were asked on campus or online to fill out the questionnaire. The answers were automatically gathered in Google Sheets and from there converted to csv and rds using /R/01-data_download.R .

# Results

Figures and tables in Results section are interpreted with 2 to 3 sentences each.

## Respondents

In the first section, respondents were asked to state their age, study field and level, and their institution. In @fig-respondents-institution (a), we can see that most answers came from people within Engineering at ETH, and that all respondents were in their 20s as seen in @fig-respondents-institution (b).

```{r}
#| layout-ncol: 2
#| label: fig-respondents-institution
#| fig-cap: "Distribution of responses"
#| fig-subcap: 
#|   - "Institutions of respondents"
#|   - "Age distribution of respondents"
#| warning: false

ggplot(data = df, 
       mapping = aes(x = reorder(institution, institution, length),
                     fill = field)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Institution",
       y = "Number of responses",
       fill = "Study field") +
  theme_minimal() +
  scale_fill_colorblind()

ggplot(data = df) +
  geom_bar(mapping = aes(x = age,
                     fill = field)) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  labs(x = "Age",
       y = "Number of responses",
       fill = "Study field") +
  theme_minimal() +
  scale_fill_colorblind() +
  geom_boxplot(mapping = aes(x = age), alpha = 0.2, position = position_nudge(y=3.5), width = 2)

```

In @fig-respondents-detail, the study level is added as well, showing us that most respondents are indeed studying Engineering at Bachelor's or Master's level at ETH Zürich, with very few outliers.

```{r}
#| label: fig-respondents-detail
#| fig-cap: "Position, Institution, Age and Field of Respondents"
#| warning: false

df <- df |> 
  mutate(position = factor(position, levels = c("Bachelor (BSc/BA)", "Master (MSc/MA)", "PhD / Doctorate", "Employee")))

ggplot(data = df, 
       mapping = aes(x = position,
                     y = age,
                     color = field)) +
  geom_jitter(size = 3, alpha = 0.6, width = 0.3, height = 0.2) +
  coord_flip() +
  labs(x = "Study level",
       y = "Age",
       color = "Field of Study / Work") +
  facet_wrap(~institution) +
  theme_minimal() +
  scale_color_colorblind()

```

In the next questions, the respondents were asked to rank 1) the general importance of waste reduction and 2) the general importance of recycling on a scale of 1 (not important at all) to 5 (very important). The answers are summarized in @fig-respondents-opinions, where it can be seen that both are perceived as important by most, with waste reduction having a higher mean importance than recycling.

```{r}
#| label: fig-respondents-opinions
#| fig-cap: "Opinions on waste reduction and recycling in general"
#| warning: false


ggplot(data = df) +
  geom_jitter(mapping = aes(x = importance_waste_reduction,
                     y = importance_recycling,
                     color = field),
              size = 3, alpha = 0.6, width = 0.25, height = 0.25) +
  geom_boxplot(mapping = aes(x = importance_waste_reduction),
               alpha = 0.2, position = position_nudge(y=1.75), width = 0.75) +
  geom_boxplot(mapping = aes(y = importance_recycling),
               alpha = 0.2, position = position_nudge(x=1.75), width = 0.75) +
  labs(x = "General importance of waste reduction",
       y = "General importance of recycling",
       color = "Field of Study / Work") +
  theme_minimal() +
  scale_color_colorblind()

```

## Single-use cup habits

When asked about their habits with buying drinks single-use cups on campus, most respondents answered that they never or occasionally bought single-use cups, and if they did, the overwhelming majority choose "convenience" as their main reason as seen in @fig-habits.

```{r}
#| label: fig-habits
#| fig-cap: "Single-use cup usage frequency and main reason"
#| warning: false


df <- df |> 
  mutate(singleusecup_frequency = factor(singleusecup_frequency, levels = c("I don't know", "Multiple times per day", "Every day", "About once a week", "Occasionally", "Never"))) |> 
  mutate(singleusecup_reason = factor(singleusecup_reason, levels = c("Convenience", "Hygiene", "Aesthetics", "Price (single-use cups are free as opposed to multi-use cups)", "I don't think about it", "I never use single-use cups")))

ggplot(data = df,
       mapping = aes(x = singleusecup_frequency,
                     fill = singleusecup_reason)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_fill_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "How often do you buy single-use cups on campus?",
       y = "Number of responses",
       fill = "Main reason") +
  theme_minimal()


```

Depending on personal preferences or other factors, a ban on single-use cups can have an impact on daily life. When asked to rank this impact on a scale of 1 ("I wouldn't notice") to 5 ("It would have a negative impact on my daily life"), most respondents answered 1 ("I wouldn't notice") as seen in @fig-impact (a). In @fig-impact (b) these results are complemented with the previous answer about the usage frequency, revealing that generally - the more respondets bought drinks in single-use cups, the higher they would consider the negative impact on their daily life.

```{r}
#| label: fig-impact
#| fig-cap: "The negative impact on daily life of a ban on single-use cups"
#| layout-ncol: 2
#| fig-subcap: 
#|   - "Ban impact on daily life with main reason"
#|   - "Ban impact on daily life with usage frequency"
#| warning: false

ggplot(data = df) +
  geom_bar(mapping = aes(x = singleusecup_ban_impact,
                     fill = singleusecup_reason)) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_impact), color = "red",
               alpha = 0.2, position = position_nudge(y=2.75), width = 3) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "How would a ban impact your daily life?",
       y = "Number of responses",
       fill = "Main reason") +
  theme_minimal() +
  scale_fill_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups"))



ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_impact,
                            y = singleusecup_frequency,
                            color = singleusecup_reason),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_impact),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "How would a ban impact your daily life?",
       y = "How often do you buy single-use cups on campus?",
       color = "Main reason") +
  theme_minimal()


```

## Opinions on a ban on single-use cups

Lastly, what do respondents think about a ban on single-use cups? The question here was "Would you support a campus-wide ban on single-use cups at cafes, kiosks, cafeterias etc?", and the answer could be given on a scale from 1 ("No, absolutely not") to 5 ("Yes, absolutely").

```{r}
#| label: fig-support
#| fig-cap: "Opinions on a ban on single-use cups"
#| layout-ncol: 2
#| layout-nrow: 2
#| fig-subcap: 
#|   - "Ban impact on daily life with main reason"
#|   - "Ban impact on daily life with usage frequency"
#| warning: false

ggplot(data = df) +
  geom_bar(mapping = aes(x = singleusecup_ban_support,
                     fill = singleusecup_reason)) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support), color = "red",
               alpha = 0.2, position = position_nudge(y=2.75), width = 3) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Support for a ban on single-use cups from 1 to 5",
       y = "Number of responses",
       fill = "Main reason") +
  theme_minimal() +
  scale_fill_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups"))



ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_support,
                            y = singleusecup_frequency,
                            color = singleusecup_reason),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  geom_smooth(mapping = aes(x = singleusecup_ban_support,
                            y = singleusecup_frequency), alpha = 0.2) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "Support for a ban on single-use cups from 1 to 5",
       y = "How often do you buy single-use cups on campus?",
       color = "Main reason") +
  theme_minimal()

ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_support,
                            y = singleusecup_ban_impact,
                            color = singleusecup_reason),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  geom_boxplot(mapping = aes(y = singleusecup_ban_impact),
               alpha = 0.2, position = position_nudge(x=0.75), width = 0.5) +
  geom_smooth(mapping = aes(x = singleusecup_ban_support,
                            y = singleusecup_ban_impact), alpha = 0.2) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "Support for a ban on single-use cups from 1 to 5",
       y = "Negative impact on daily life",
       color = "Main reason") +
  theme_minimal()


```

Now, if we look at support in terms of study program and field, we can see no direct trend or tendency, but a wide range of opinions @fig-support-study (a) and (b). This is probably also due to insufficient and non-respresentative data, but also reflects the fact that this topic is quite

```{r}
#| label: fig-support-study
#| fig-cap: "Opinions on a ban on single-use cups based on study program and field"
#| layout-ncol: 2
#| warning: false
#| fig-subcap: 
#|   - "Support for a ban based on study field"
#|   - "Support for a ban based on study program"

ggplot(data = df) +
  geom_bar(mapping = aes(x = singleusecup_ban_support,
                     fill = field)) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(y=2.75), width = 3) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Support for a ban on single-use cups from 1 to 5",
       y = "Number of responses",
       fill = "Study field") +
  theme_minimal() +
  scale_fill_colorblind()



ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_support,
                            y = position,
                            color = field),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_support),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind() +
  labs(x = "Support for a ban on single-use cups from 1 to 5",
       y = "Study program",
       color = "Study field") +
  theme_minimal()


```

```{r}
#| label: fig-options
#| fig-cap: "Without single-use cups, what alternatives or options need to be available?"
#| warning: false


df <- df |> 
  mutate(options_bring_own_cup = factor(options_bring_own_cup, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_sit_down = factor(options_sit_down, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_none = factor(options_none, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_multiusecup_small_deposit = factor(options_multiusecup_small_deposit, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_multiusecup_large_deposit = factor(options_multiusecup_large_deposit, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know"))) |> 
  mutate(options_multiusecup_to_buy = factor(options_multiusecup_to_buy, levels = c("Absolutely", "Preferably", "Maybe", "Not at all", "I don't know")))

df_options <- df |> 
  select(id, singleusecup_ban_support, singleusecup_ban_impact, options_bring_own_cup:options_none) |> 
  pivot_longer(cols = options_bring_own_cup:options_none,
               names_to = "option",
               values_to = "opinion") |> 
  mutate(option = factor(option, levels = c("options_none", "options_multiusecup_large_deposit", "options_multiusecup_to_buy", "options_multiusecup_small_deposit", "options_sit_down", "options_bring_own_cup")))

color_values <- scales::seq_gradient_pal("blue", "orange", "Lab")(seq(0,1,length.out=5))

ggplot(data = df_options,
       mapping = aes(x = option,
                     fill = opinion)) +
  geom_bar() +
  coord_flip() +
  scale_x_discrete(labels = c("No option; you have to bring your own cup", "Multi-use cups with a large deposit (> 5 Fr.)", "Multi-use cups that you have to buy (> 10 Fr.)", "Multi-use cups with a small deposit (< 5 Fr.)", "Sit down with ceramic cups at no extra costs", "You can bring your own cup")) +
  labs(x = "Option",
       y = "Number of answers",
       fill = "Opinion") +
  theme_minimal() +
  scale_fill_manual(values = color_values)


```

# Conclusions

Conclusions concisely summarize findings in a bullet point format.

-   aosbasda

-   asdasda

-   sdasdas

-   daasd
