---
title: "What do students think about a campus-wide ban on signle-use cups at cafeterias and kiosks?"
subtitle: "Analysis of a non-representative survey of students in Zurich"
date: 2024-06-06
author:
  - name: Till Häussner
    orcid: 0009-0005-7617-9312
    email: thaeussner@student.ethz.ch
    affiliation: 
      - name: ETH Zürich
        url: www.ethz.ch
abstract: > 
  
keywords:
  - Waste Reduction
  - Single-Use Cups
  - Students
  - University Campus
  
format:
  html:
    toc: true
    html-math-method: katex
    css: styles.css
    

license: "CC BY"
funding: "The author received no specific funding for this work."
---

```{r}
#| echo: FALSE

library(tidyverse)
library(scales)
library(ggthemes)
library(ggExtra)

df <- read_rds(here::here("data/processed/processed_data.rds"))


```

# Introduction

Introduction section with 3 to 5 sentences introduces the context within which the data was created.

# Methods

Methods section describes in 3 to 5 sentences how the data was obtained.

# Results

Figures and tables in Results section are interpreted with 2 to 3 sentences each.


```{r}
#| layout-ncol: 2
#| label: fig-respondents-institution
#| fig-cap: "Distribution of responses"
#| fig-subcap: 
#|   - "Institutions of respondents"
#|   - "Age distribution of respondents"

ggplot(data = df, 
       mapping = aes(x = reorder(institution, institution, length),
                     fill = field)) +
  geom_bar() +
  coord_flip() +
  labs(x = "Institution",
       y = "Number of responses") +
  theme_minimal() +
  scale_fill_colorblind() +
  theme(legend.position = "none")

ggplot(data = df,
       mapping = aes(x = age,
                     fill = field)) +
  geom_bar() +
  labs(x = "Age",
       y = "Number of responses",
       fill = "Field of Study / Work") +
  theme_minimal() +
  scale_fill_colorblind()
```

```{r}
#| label: fig-respondents-detail
#| fig-cap: "Position, Institution, Age and Field of Respondents"

df <- df |> 
  mutate(position = factor(position, levels = c("Bachelor (BSc/BA)", "Master (MSc/MA)", "PhD / Doctorate", "Employee")))

ggplot(data = df, 
       mapping = aes(x = position,
                     y = age,
                     color = field)) +
  geom_jitter(size = 3, alpha = 0.6, width = 0.3, height = 0.2) +
  coord_flip() +
  labs(x = "Position",
       y = "Age",
       color = "Field of Study / Work") +
  facet_wrap(~institution) +
  theme_minimal() +
  scale_color_colorblind()

```


# Conclusions

Conclusions concisely summarize findings in a bullet point format.

-   aosbasda

-   asdasda

-   sdasdas

-   daasd
