---
title: "What do students think about a campus-wide ban on signle-use cups at cafeterias and kiosks?"
subtitle: "Analysis of a non-representative survey of students in Zurich"
date: 2024-06-06
author:
  - name: Till Häussner
    orcid: 0009-0005-7617-9312
    email: thaeussner@student.ethz.ch
    affiliation: 
      - name: ETH Zürich
        url: www.ethz.ch
abstract: > 
  
keywords:
  - Waste Reduction
  - Single-Use Cups
  - Students
  - University Campus
  
format:
  html:
    code-fold: true
    toc: true
    html-math-method: katex
    css: styles.css
    
    

license: "CC BY"
funding: "The author received no specific funding for this work."
---

```{r}
#| warning: false

library(tidyverse)
library(scales)
library(ggthemes)
library(ggExtra)

df <- read_rds(here::here("data/processed/processed_data.rds"))



```

# Introduction

Introduction section with 3 to 5 sentences introduces the context within which the data was created.

# Methods

The data was obtained using a Google Forms survey. Over the span of nine days from 2024-05-21 to 2024-05-29, students were asked on campus or online to fill out the questionnaire. The answers were automatically gathered in Google Sheets and from there converted to csv and rds using /R/01-data_download.R .

# Results

Figures and tables in Results section are interpreted with 2 to 3 sentences each.

## Respondents

In the first section, respondents were asked to state their age, study field and level, and their institution. In @fig-respondents-institution (a), we can see that most answers came from people within Engineering at ETH, and that all respondents were in their 20s as seen in @fig-respondents-institution (b).
```{r}
#| layout-ncol: 2
#| label: fig-respondents-institution
#| fig-cap: "Distribution of responses"
#| fig-subcap: 
#|   - "Institutions of respondents"
#|   - "Age distribution of respondents"

ggplot(data = df, 
       mapping = aes(x = reorder(institution, institution, length),
                     fill = field)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "Institution",
       y = "Number of responses") +
  theme_minimal() +
  scale_fill_colorblind() +
  theme(legend.position = "none")

ggplot(data = df) +
  geom_bar(mapping = aes(x = age,
                     fill = field)) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  labs(x = "Age",
       y = "Number of responses",
       fill = "Field of Study / Work") +
  theme_minimal() +
  scale_fill_colorblind() +
  geom_boxplot(mapping = aes(x = age), alpha = 0.2, position = position_nudge(y=3.5), width = 2)

```
In @fig-respondents-detail, the study level is added as well, showing us that most respondents are indeed studying Engineering at Bachelor's or Master's level at ETH Zürich, with very few outliers.

```{r}
#| label: fig-respondents-detail
#| fig-cap: "Position, Institution, Age and Field of Respondents"

df <- df |> 
  mutate(position = factor(position, levels = c("Bachelor (BSc/BA)", "Master (MSc/MA)", "PhD / Doctorate", "Employee")))

ggplot(data = df, 
       mapping = aes(x = position,
                     y = age,
                     color = field)) +
  geom_jitter(size = 3, alpha = 0.6, width = 0.3, height = 0.2) +
  coord_flip() +
  labs(x = "Study level",
       y = "Age",
       color = "Field of Study / Work") +
  facet_wrap(~institution) +
  theme_minimal() +
  scale_color_colorblind()

```
In the next questions, the respondents were asked to rank 1) the general importance of waste reduction and 2) the general importance of recycling on a scale of 1 (not important at all) to 5 (very important). The answers are summarized in @fig-respondents-opinions, where it can be seen that both are perceived as important by most, with waste reduction having a higher mean importance than recycling.

```{r}
#| label: fig-respondents-opinions
#| fig-cap: "Opinions on waste reduction and recycling in general"


ggplot(data = df) +
  geom_jitter(mapping = aes(x = importance_waste_reduction,
                     y = importance_recycling,
                     color = field),
              size = 3, alpha = 0.6, width = 0.25, height = 0.25) +
  geom_boxplot(mapping = aes(x = importance_waste_reduction),
               alpha = 0.2, position = position_nudge(y=1.75), width = 0.75) +
  geom_boxplot(mapping = aes(y = importance_recycling),
               alpha = 0.2, position = position_nudge(x=1.75), width = 0.75) +
  labs(x = "General importance of waste reduction",
       y = "General importance of recycling",
       color = "Field of Study / Work") +
  theme_minimal() +
  scale_color_colorblind()

```
## Single-use cup habits

Respondents were then asked about their usage of single use cups and how much a ban would affect them in daily life.

```{r}
#| label: fig-habits
#| fig-cap: "Single-use cup usage frequency and main reason"


df <- df |> 
  mutate(singleusecup_frequency = factor(singleusecup_frequency, levels = c("I don't know", "Multiple times per day", "Every day", "About once a week", "Occasionally", "Never"))) |> 
  mutate(singleusecup_reason = factor(singleusecup_reason, levels = c("Convenience", "Hygiene", "Aesthetics", "Price (single-use cups are free as opposed to multi-use cups)", "I don't think about it", "I never use single-use cups")))

ggplot(data = df,
       mapping = aes(x = singleusecup_frequency,
                     fill = singleusecup_reason)) +
  geom_bar() +
  coord_flip() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_fill_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "How often do you buy single-use cups on campus?",
       y = "Number of responses",
       fill = "Main reason") +
  theme_minimal()


```

```{r}
#| label: fig-impact
#| fig-cap: "Single-use cup usage frequency and main reason"
#| #| layout-ncol: 2
#| fig-subcap: 
#|   - "Ban impact on daily life with main reason"
#|   - "Ban impact on daily life with usage frequency"

ggplot(data = df, 
       mapping = aes(x = singleusecup_ban_impact,
                     fill = singleusecup_reason)) +
  geom_bar() +
  scale_y_continuous(breaks = seq(from = 0, to = 100, by = 2)) +
  labs(x = "How would a ban impact your daily life?",
       y = "Number of responses") +
  theme_minimal() +
  scale_fill_colorblind() +
  theme(legend.position = "none")



ggplot(data = df) +
  geom_jitter(mapping = aes(x = singleusecup_ban_impact,
                            y = singleusecup_frequency,
                            color = singleusecup_reason),
              size = 3, alpha = 0.6, width = 0.2, height = 0.2) +
  geom_boxplot(mapping = aes(x = singleusecup_ban_impact),
               alpha = 0.2, position = position_nudge(y=0.75), width = 0.5) +
  scale_x_continuous(breaks = seq(from = 0, to = 100, by = 1)) +
  scale_color_colorblind(labels = c("Convenience", "Hygiene", "Aesthetics", "Price", "I never use single-use cups")) +
  labs(x = "How would a ban impact your daily life?",
       y = "How often do you buy single-use cups on campus?",
       color = "Main reason") +
  theme_minimal()


```


## Opinions on a ban on single-use cups

Lastly, what do respondents think about a ban on single-use cups?



# Conclusions

Conclusions concisely summarize findings in a bullet point format.

-   aosbasda

-   asdasda

-   sdasdas

-   daasd
